\tname: A Database of Reproducible Bugs in Deep Learning Libraries to Enable Systematic Evaluation of Testing Techniques

### 2025-03-20 paper/main.tex
Added contribution steps

\begin{enumerate}[leftmargin=0.5cm]
  \item Select an issue following the criteria defined in Section~\ref{sec:selection-criterion};
  \item Write file \CodeIn{requirements.txt} with the list of dependencies to reproduce the bug; \Fix{Clarify that the version of the library which was used to report the bug is also included in the requirements.txt file}
  \item Create a file showing the code that causes the bug (for documentation);
  \item Create a file with a \CodeIn{pytest} test case that passes if
    the code triggers the buggy behavior documented in the issue;
    %% A python file is created that contains the bug revealing code, along with a test (pytest) that passes upon successfully trigerring the buggy behavior.
  \item If the bug depends on a CUDA-specific build, write a
    Dockerfile to create a container including the needed CUDA-driver
    and the other artifacts mentioned above (e.g., test file and
    requirements);
    %% along with the requirements.txt file and the python
    %% script copied into it.
  \item Write a script that creates the virtual environment (either
    Python's \CodeIn{Conda Enviroment}~\cite{venv} or Docker container) and runs
    the test on it;
  \item Create a directory \CodeIn{<lib>/<bug-id>} containing all the
    artifacts mentioned above, where \CodeIn{lib} refers to the
    affected library and \CodeIn{bug-id} is a fresh identifier of the
    bug instance.
    %% All files are put into a single self-contained folder with the issue id in the name so that the tools exposed by the framework of our tool can find and execute the the bug reproduction script.
\end{enumerate}

@@

>>>>

\begin{enumerate}[leftmargin=0.5cm]
  \item Select an issue following the criteria defined in Section~\ref{sec:selection-criterion};
  \item Identify the version of the library used to report the bug along with other dependencies;
  \item Write a \CodeIn{requirements.txt} file with the list of dependencies to reproduce the bug;
  \item Create a file showing the code that causes the bug (for documentation);
  \item Create a file with a \CodeIn{pytest} test case that passes if
    the code triggers the buggy behavior documented in the issue;
    %% A python file is created that contains the bug revealing code, along with a test (pytest) that passes upon successfully trigerring the buggy behavior.
  \item If the bug depends on a CUDA-specific build, write a
    Dockerfile to create a container including the needed CUDA-driver
    and the other artifacts mentioned above (e.g., test file and
    requirements);
    %% along with the requirements.txt file and the python
    %% script copied into it.
  \item Write a script that creates the virtual environment (either
    Python's \CodeIn{Conda Enviroment}~\cite{venv} or Docker container) and runs
    the test on it;
  \item Create a directory \CodeIn{<lib>/<bug-id>} containing all the
    artifacts mentioned above, where \CodeIn{lib} refers to the
    affected library and \CodeIn{bug-id} is a fresh identifier of the
    bug instance.
    %% All files are put into a single self-contained folder with the issue id in the name so that the tools exposed by the framework of our tool can find and execute the the bug reproduction script.
\end{enumerate}

@@

\subsection{Contribution}

\tname\ allows users to contribute to the dataset by adding new bug
instances. This opens up the tool to the community to help in
expanding the dataset and improving the quality of the dataset.
The following steps show how to contribute a new bug
instance:

\begin{enumerate}[leftmargin=0.5cm]
  \item Identify issues in the issue tracker of the library of interest;
  \item Create an issue in the repository of \tname\ with the template
    "Reproduce Bug" (available in the repository);
  \item Create a branch linked to the issue;
  \item Add a self-contained bug reproduction script in a sub-directory
    named with the GitHub issue identifier under the directory of the library;
  \item Prepare the execution environment (Docker containers~\cite{merkel2014docker} for CUDA-dependent
    bugs, \CodeIn{Conda Enviroment}~\cite{venv} for others);
  \item Follow the steps in \ref{sec:method} to create the bug reproduction script;
  \item Update the spreadsheets of the library with bug details;
  \item Create a pull request to the main branch.
\end{enumerate}

\Fix{Abid: Added, please revise}
